Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-17 paper/manuscript.tex
Some additions to manuscript

Despite the similarities in the epitope-targeting of C179 and FI6v3, we also see selection for distinct escape mutations with either antibody.
The mutation with the strongest effect size from selection by C179 occurs at site 38, while we do not see observable escape mutations at this site by selection with FI6v3.
Interestingly, we found that HA subtypes susceptible to binding or neutralization by C179 tend to possess a histidine at this site, but subtypes not bound or neutralized by C179 possess a glutamine or serine (Figure~\ref{fig:structures}C). 
This would suggest that susceptibility to neutralization by C179 may in part be determined by the amino-acid identity at site 38.
Furthermore, the difference in breadth between C179 and FI6v3 has been attributed to FI6v3 being able to accommodate a glycan on the Asn at site 38 which is present in group 2 but not group 1 HA's, while group 1-specific stalk-targeting antibodies clash with this glycan~\citep{corti2011neutralizing, sui2009structural, ekiert2009antibody}. 
The H38S mutation selected by C179 does not introduce a glycosylation motif, which indicates that introduction of a glycan at this site is not the only means of mediating escape from this group 1-specific anti-stalk antibody.

>>>>

Despite the similarities in the epitope-targeting of C179 and FI6v3, we also see selection for distinct escape mutations with either antibody.
The mutation with the strongest effect size from selection by C179 occurs at site 38, while we do not see observable escape mutations at this site by selection with FI6v3.
Interestingly, we found that HA subtypes susceptible to binding or neutralization by C179 tend to possess a histidine at this site, but subtypes not bound or neutralized by C179 possess a glutamine or serine (Figure~\ref{fig:structures}C). 
This would suggest that susceptibility to neutralization by C179 may in part be determined by the amino-acid identity at site 38.
Furthermore, the difference in breadth between C179 and FI6v3 has been attributed to FI6v3 being able to accommodate a glycan on the Asn at site 38 which is present in group 2 but not group 1 HA's, while group 1-specific stalk-targeting antibodies clash with this glycan~\citep{corti2011neutralizing, sui2009structural, ekiert2009antibody}. 
The H38S mutation selected by C179 does not introduce a glycosylation motif, which indicates that introduction of a glycan at this site is not the only means of mediating escape from this group 1-specific anti-stalk antibody.
The amino-acid identity at site 111 of HA2 can change the orientation of a conserved Trp21 in HA2, also resulting in group 1 and group 2 differences in the binding ability of stalk-targeting antibodies. An H111T mutation in the A/South Carolina/1/1918 (H1N1) has been reported to abrogate C179 binding~\citep{dreyfus2013structure}.
However, we did not observe escape mutations at site 111, but this may be due to strain-specific differences
